Results

### 2024-04-23 Analysis/04_Summarise_results.Rmd
Update 04_Summarise_results.Rmd

>>>>

```{r}
## The plot
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_4d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_4d, col = col_vector, lm = model_fits_4d, null = null_differences_4d, metric.names = fancy_names)
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_5d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_5d, col = col_vector, lm = model_fits_5d, null = null_differences_5d, metric.names = fancy_names)
dev.off()
```

```{r}
## The plot
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names)

## Pdf version
pdf(file = "../Manuscript/Figures/results_per_metric_per_stressor_8d.pdf", height = 9, width = 9)
fancy.plot(scaled_results_8d, col = col_vector, lm = model_fits_8d, null = null_differences_8d, metric.names = fancy_names)
dev.off()
```
